### 2014-12-29 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: edits to report

@@

>>>>

Figures~\ref{fig:int_temp_99s} to \ref{fig:int_temp_142s} show two interior views of temperature contours at particular snapshots in time. The top image is a planar view through the middle of the front door (from the front to the back of the house) which shows the conditions in the living area on the first floor and the conditions in the basement just past the bottom of the stairs. The bottom image shows temperature contours through the middle of the interior stairwell which connected the basement to the first floor of the structure (looking from the rear of the structure towards the front). Prior to the front door being opened (Fig.~\ref{fig:int_temp_99s}, temperatures in excess of 200~$^{\circ}$C (400~$^{\circ}$F) were confined to basement of the structure: specifically the rear of the structure and under the stairwell. One second after the door was opened, hazard in the structure increased within the structure with the most drastic change occurring at the top of the stairwell as peak simulated temperatures exceeded 400~$^{\circ}$C (750~$^{\circ}$F). At the approximate time firefighters made entry to the first floor, Fig.~\ref{fig:int_temp_142s}, the conditions within the flowpath (interior stairwell through front door) had become more severe with temperatures in excess of 400~$^{\circ}$C (750~$^{\circ}$F), which exceeds the Class III exposure of 260~$^{\circ}$C (500~$^{\circ}$F). These high-hazard conditions within the flowpath remained until the model HRR was reduced to simulate the action of applying water the fire.

@@

Based on these results and the simulation results shown in Sections~\ref{velocity} and \ref{temp}, after the front door was opened, the simulated flow path temperatures in the interior stairwell were in excess of 400~$^{\circ}$C (750~$^{\circ}$F) and the flow velocities were in excess of 9 m/s (20 mph). The conditions in the interior stairwell changed from tenable to high-hazard very rapidly following the opening of the front door. Within the structure, the hot gases and smoke were moving along the flow path from the basement towards the door located on the front side of the structure via the interior stairwell. The simulated temperatures are consistent with the post-incident conditions that were documented in the interior stairwell.

Ongoing research and experimental work is being conducted by NIST to gain a better understanding of convective heat transfer to firefighter personal protective equipment, including firefighting gear, helmets, self-contained breathing apparatuses, etc. The goal of this ongoing research is to parameterize various flow path conditions (elevated temperatures and velocities) and determine their effect on the rate of heat transfer and amount of energy storage in firefighting safety equipment.
